Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-02-07 ForegroundSimulations/ms.tex
Add discussion about pitchfork effect in section 3
From ace91c7 (master):
=====================

In ms.tex,

(*) Add discussion about pitchfork effect in section 3

\subsection{The Wide-Field ``Pitchfork'' Effect}\label{sec:wide-field}

\citep{thy15a,thy15b}

@@

We simulate wide-field visibilities for 19-element HERA from all-sky antenna power pattern and foreground models using the PRISim\footnote{The Precision Radio Interferometry Simulator (PRISim) is publicly available at \href{https://github.com/nithyanandan/PRISim}{https://github.com/nithyanandan/PRISim}} software package. The simulations cover 24~hr of observation in {\it drift} mode consisting of 80 accumulations spanning 1080~s each. The total bandwidth is 100~MHz centered on 150~MHz consisting of 128 channels with 781.125~kHz frequency resolution each. Models of the antenna power pattern and foregrounds are described below.

>>>>

It was recently discovered that in wide-field measurements diffuse foreground emission from wide off-axis angles appear enhanced in the delay spectrum near the edges of the {\it foreground wedge} even on wide antenna spacings \citep{thy15a}. Called the {\it pitchfork} effect, this arises due to severe foreshortening of baseline vectors towards the horizon along joining the antenna pairs thereby enhancing their sensitivity to large scale structures in these directions. Since delay spectrum maps directions on the sky to delay bins, the emission from large scales near the horizon appears enhanced in delay bins near the horizon limits of the {\it foreground wedge}. Since these delay modes lie adjacent to those considered sensitive to the EoR signal, they cause a significant contamination of line-of-sight modes critical for EoR signal detection. These findings were confirmed in MWA observations \citep{thy15b}.

It was also demonstrated in these studies that design of antenna power pattern, specifically its amplitude near the horizon, is an important tool in mitigating foreground contamination caused by these wide-field effects. A dish characterized by a nominal {\it Airy} pattern was found to mitigate this contamination by over four and two orders of magnitude relative to a dipole and a phased array of dipoles respectively. HERA has significantly based its antenna design principles on these findings in choosing its antenna geometry while paying close attention to the properties of the resulting antenna power pattern.

In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections between the dish-receiver assembly to within tolerable limits.

@@

We simulate wide-field visibilities for 19-element HERA from all-sky antenna power pattern and foreground models using the PRISim\footnote{The Precision Radio Interferometry Simulator (PRISim) is publicly available at \href{https://github.com/nithyanandan/PRISim}{https://github.com/nithyanandan/PRISim}} software package. The simulations cover 24~hr of observation in {\it drift} mode consisting of 80 accumulations spanning 1080~s each. The total bandwidth is 100~MHz centered on 150~MHz consisting of 256 channels with 390.625~kHz frequency resolution. Models of the antenna power pattern and foregrounds are described below.
